\section{Nussinov}
\label{sec:nussinov}
We now introduce the algorithm of nussinov,
which is a basic Dynamic Programming algorithm which was one of the first attempts at predicting the structure of RNA molecules computationally.
The nussinov algorithm get a RNA sequence as input.
The aim of the algorithm is to find out the pairings of the nucleotides in the sequence and compute a optimal structure.
We can break down the problem into many subproblems which are easier to compute than the full problem. Once we have obtained the solution for the subproblems,
we can retrieve the solution to the full problem by doing a backtrace.
In order to know how good our structure is, we assign a score to it.
One possible scoring scheme could be adding 1 to the score per paired set of nucleotides,
and 0 otherwise. We want a pairing that will give us the highest possible score.
This quantity we call $score(i,j)$, where $i,j$ are the indices of the sequence between which we obtain the pairing score.
The nussinov algorithm computes a folding score for all substrings
bound by $i$ and $j$ and store the value in what is known as a
dynamic programming matrix. The matrix has shape $N \times N$, $N$ is the length of the input sequence.
We need a way to evaluate scores given a subsequence. To do this, we set some rules on the structure of an RNA sequence:
If $i$ and $j$ form a pair:
(1) The pair $i$ and $j$ must form a valid watson-crick pair.
(2) $i<j-4$. This ensures that bonding is not happening between positions that are too close to each other, which would produce steric clashes.
(3) If pair $(i,j)$ and $(k,l)$ are in the structure, then $i<k<j<l$. This ensures that there is no crossing over of pairs which would result in pseudoknots.
(4) No base appears in more than one pair.

The workflow of the algorithm is a s follows:
\begin{enumerate}
  \item Initialize the matrix $D$.
  \item fill the matrix $D$ recursively by following the following recursion:
  $$matrix[i][j] = \begin{cases}0 \text{ if } i >= j - min_loop_length\\
  max(unpaired, paired) \text{ else}
  \end{cases} $$
  where $unpaired$ is the score of letters i,j-1, $$unpaired = score(i, j - 1, sequence)$$
  $paired$ is the score of pairing letter at j,
  $paired = [ 1 + score(i, k - 1) + score(k + 1, j - 1) | \text{ for  k in range } (i, j - 4), \text{ if } sequence[k] \text{ and } sequence[j]  \text{ is a basepair}]$
  \item traceback recursively starting at $i=0,j=N$.
  if $j$ is unpaired, there will be no change in score when we take it out, so we just recurse to the next index.
  if the score at $i,j$ is the result of adding 1 from pairing $(j,k)$ and whatever score
   comes from the substructure to its left $(i, k-1)$ and to its right $(k+1, j-1)$.
   if $k-1 < 0$ and  $matrix[i][j] == matrix[k + 1][j - 1] + 1$, we add $k,j$ to our structure,
   and traceback from $k+1$, $j-1$.
   If $k -1 >= 0$, and $matrix[i][j] == self.matrix[i][k - 1] + matrix[k + 1][j - 1] + 1$, we append $k,j$ to our structure, and explore from $i,k-1$  and $k+1,j-1$

\end{enumerate}
